\sectionTitle{Research Experience}{}

\begin{experiences}

\researchexperience
    {Present}   {Google Research | Machine Learning and Optimization {\normalfont  ~ [\href{https://research.google/teams/india-research-lab/}{\small{\websiteSymbol}}]
    }}{Bangalore, India}{Bangalore, India}
    {Jul 2021} {\textit{Pre-Doctoral Researcher | Advisor:  \href{https://research.google/people/107631/}{Dr. Aravindan Raghuveer}}\\
    Exploring Natural Language Generation techniques for creative advertisement generation. Investigating several research areas like text style transfer, data-to-text generation, semantic representations etc.
    \vskip 0.1cm
    }
  \emptySeparator
    \researchexperience
    {Aug 2020}   {GREYC Lab, ENSI-CAEN{\normalfont  ~ [\href{https://www.ensicaen.fr/en/research/greyc/}{\small{\websiteSymbol}}]
    }}{Remote / Caen, France}{}
    {Jul 2020} {\textit{Research Intern | Advisor: \href{https://dias.users.greyc.fr/}{Prof. Gaël Dias}}\\
    Extended patch-based lexical semantic identification frameworks to a multi-modal setting. Developed the dataset and conducted the pilot studies of the project. [\textit{ACM MM'22}]
    }
%   \emptySeparator
%   \researchexperience
%     {Jan 2020}   {TCS Innovation Lab {\normalfont  ~ [\href{https://www.tcs.com/research-and-innovation}{\small{\websiteSymbol}}]
%     }}{Kolkata, India}{}
%     {Dec 2019} {\textit{Research Intern | Advisor: \href{https://www.linkedin.com/in/arijitukil}{Arijit Ukil}}\\
%     Investigated generative modeling to tackle the insufficiency of data in time-series signal classification.
%     }
  \emptySeparator
   \researchexperience
    {Jun 2019}   {Graduate School of Informatics, Kyoto University {\normalfont  ~ [\href{http://www.i.kyoto-u.ac.jp/en/}{\small{\websiteSymbol}}]
    }}{Kyoto, Japan}{}
    {May 2019} {\textit{Research Intern | Advisor: \href{https://adammo12.github.io/adamjatowt/}{Prof. Adam Jatowt}}\\
    Explored various unsupervised optimization techniques to develop multi-modal summarization systems that generate text-image-audio-video summaries. % Work from this collaboration accepted in ECIR'20 (short), SIGIR'20 (short), and SIGIR'21.
    }
  \emptySeparator
   \researchexperience
    {Jan 2020}   {CFILT Lab, IIT Bombay {\normalfont  ~ [\href{https://www.cfilt.iitb.ac.in/}{\small{\websiteSymbol}}]
    }}{Mumbai, India}{}
    {Dec 2019} {\textit{Research Intern | Advisor: \href{https://www.cse.iitb.ac.in/~pb/}{Prof. Pushpak Bhattacharyya}}\\
    Examined Unsupervised NMT for distant language pairs (Indo-Aryan languages) using attention based seq2seq models.
    }
%   \emptySeparator
%   \researchexperience
%     {Jul 2021}   {AI-NLP-ML Lab, IIT Patna {\normalfont  ~ [\href{https://www.iitp.ac.in/~ai-nlp-ml/}{\small{\websiteSymbol}}]
%     }}{Patna, India}{}
%     {Jul 2018} {\textit{Undergraduate Research Scholar | Advisor: \href{https://www.iitp.ac.in/~sriparna/}{Dr. Sriparna Saha}}\\
%     Worked extensively in the area of summarization (\textit{e.g.,} multi-modal summarization, extractive and abstractive text summarization), and complaint mining and multi-label classification.
%     % Mentored six students (including three interns, one undergraduate student, and two masters students) as a member of the lab.
%     }
    
  
\end{experiences}
\vspace{-4mm}
